AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-02-14 article/tex/submission.tex
polishes abstract

%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{AIR4children: Artificial Intelligence and Robotics for Children}
%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{Lastname et al.}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In this work, we proposed air4children, artificial intelligence for children as a way to both (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create a child-centre approach for AI and robotics.
We introduce the present current challenges and opportunities for a child-centre approach for AI and robotics. 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
Then, we describe the avenues that air4children can work with as development of open-sourced software and hardware, open-sourced teaching material. 
Finally, we add conclusions and future work. 
\end{abstract}

@@

\section{Introduction} 
The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade, specially in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
However, such support brings other challenges such as the little to none focus on a centered AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
In terms of a child-centered AIR, ...
Similarly, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility. 
Additionally, AIR4children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.

For this work, section 2 review open source projects as a way to minimise cost for hardware and software as the basis of the material for air4children which is presented in section 3. 
Then, we conclude with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.

@@

\begin{table}
  \begin{tabular}{ccc}
    \toprule
    Project & Established  & Cost\\
    \midrule
    JPL Open Source Rover \cite{OSR:2018} & April 2018  &  USD 2500.00 \\
    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019  & EUROS 212.00    \\
    Otto DIY robots \cite{OttoDIY:2016} & 2016 &  EUROS 100.00  \\
    Robot at air4children & 2021 & EUROS 100.00  \\
  \bottomrule
\end{tabular}
\caption{Open source projects for educational AI and Robotics}
\label{tab:opensourceprojects}
\end{table}

@@

In a first phase, air4children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the participants. 
This initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.

@@

\subsection{Open source hardware and software}
Adopting the philosophy of open source, air4children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of air4children are in the range of EURO 100.00. 
Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recognise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).

\subsection{Open teaching materials}
Considering teaching materials to be child-like oriented, air4children is then adopting Montessori's education which education philosophy orbited around this quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for air4children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) \cite{bers2012, resnick1998}.
Similarly, Elkin et al. (2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adopted for air4children to reinforce the above Montessori skills \cite{tarik2017}.

%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity. 
%In that way, air4children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
  \caption{(a) Spiral learning divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
  %\Description{.}
  \label{fig:tm}
\end{figure}

@@

\section{Conclusions and future work}
We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create a more child-centre approach for AI and Robotics.
In this work, we also touched on the open source projects in AI and Robotics as a corner stone for air4children with the aim of minimise cost of the materials and made customised educational material.  
Similarly, it has been presented the three phases for air4children for piloting, implementing and refining workshops for children in the age range between 6 to 14. 
We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills such as think creatively with curiosity and open-minded as well as develop a have a sense of wonder and joy in learning.

>>>>

%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{AIR4Children: Artificial Intelligence and Robotics for Children}
%%
%% The "author" command and its associated commands are used to define
%% the authors and their affiliations.
%% Of note is the shared affiliation of the first two authors, and the
%% "authornote" and "authornotemark" commands
%% used to denote shared contribution to the research.

@@

%%
%% By default, the full list of authors will be used in the page
%% headers. Often, this list is too long, and will overlap
%% other information printed in the page headers. This command allows
%% the author to define a more concise list
%% of authors' names for this purpose.
\renewcommand{\shortauthors}{air4children}

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
In this work, we proposed AIR4Children, artificial intelligence for children, as a way to (a) tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation and (b) to create affordable child-centred materials in AI and robotics.
We present current challenges and opportunities for a child-centred approaches for AI and robotics (AIR). 
Similarly, we touch on open-sourced software and hardware technologies to make a more inclusive, transparent and fair participation of children in areas of AIR. 
Then, we describe the avenues that AIR4Children can take with the development of open-sourced software and hardware.
Similarly, we propose to follow the philosophy of Montessori education 
to help children to not only develop matematical thinking but also to internalise new concepts and learning skills through activities of movement and repetition with open source robots.
Finally, we add conclusions and mainly we pose the future work to go of AIR4children to putting in practice what is proposed here and measure the impact on AI and robotics of children. 
\end{abstract}

@@

\section{Introduction} 
The scientific and technological progress in the fields of Artificial Intelligence and Robotics (AIR) has been rapidly moving forward over the past decade, specially in countries such as United States, China and Europe where support of such fields is part of their agenda \cite{Savage2020}. 
However, such support brings other challenges such as the little to none focus on a centered AIR for children as well as the challenge of making the fields of AIR available to under-represented communities.
In terms of a child-centered AIR, ...
Similarly, such technologies are unreachable to young audiences from under-represented communities as recently pointed out by United Nations Children's Fund (UNICEF) \cite{UNICEF2020}.
That said, this work is proposing Artificial Intelligence and Robotics for Children (AIR4Children) as a way to make AIR available to young audiences with perhaps limited resources and to creation and design tools based on open-sourced projects to address fairness and accessibility. 
Additionally, AIR4Children is aiming to design curriculums with an non-traditional education approach for children of different socio economical backgrounds, developmental stages or learning abilities.

For this work, section 2 review open source projects as a way to minimise cost for hardware and software as the basis of the material for AIR4Children which is presented in section 3. 
Then, we conclude with current status of AIR for children, open source materials for hardware, software and teaching and add few words on the future work as a way to mitigate few of the challenges cited above.

@@

\begin{table}
  \begin{tabular}{ccc}
    \toprule
    Project & Established  & Cost\\
    \midrule
    JPL Open Source Rover \cite{OSR:2018} & April 2018  &  USD 2500.00 \\
    JetBot AI Robot \cite{nanoJetBot:2019} & March 2019  & EUROS 212.00    \\
    Otto DIY robots \cite{OttoDIY:2016} & 2016 &  EUROS 100.00  \\
    Robot at AIR4Children & 2021 & EUROS 100.00  \\
  \bottomrule
\end{tabular}
\caption{Open source projects for educational AI and Robotics}
\label{tab:opensourceprojects}
\end{table}

@@

In a first phase, AIR4Children project will be piloting teaching materials with our open source robots and otto, a well known open source educational robot.  
Then in a second phase, and with feedback of the pilots, teaching materials as well as the customisation of open source robots will be improved to polish a more centred-child curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops that will be free to all the participants. 
This initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate their perception on the fields of AI and Robotics.

@@

\subsection{Open source hardware and software}
Adopting the philosophy of open source, AIR4Children is aiming to tackle the need of accessible and affordable resources for AI and Robotics to young audiences \cite{UNICEF2020}.
For instance, as a way to mitigate the hight prices of educational robots, our initial prototypes of AIR4Children are in the range of EURO 100.00. 
Such prototype, based on raspberry pi, arduino uno board and few actuators, is able to recognise voice commands in English language to move the robot in different directions (Fig \ref{fig:teaser}(a)).
Similarly, we have identified Otto robot, a DIY educational robot, which is based on arduino, servomotors and a scratch as interface to program the robot with various routines for sensors and actuators with a price of EURO 100.00 (Fig \ref{fig:tm} (b)).

\subsection{Open teaching materials}
Considering teaching materials to be child-like oriented, AIR4Children is then adopting Montessori's education which education philosophy orbited around this quote “the hand is the instrument of the mind.” \cite{montessori2013absorbent}.
In that way, materials for AIR4Children are based on Montessori education with the aim to help children to internalise new concepts and to develop concentration of their learning skills through activities of movement and repetition.
%For instance, the best way a child can concentrate is by fixing his attention on some task he is performing with his hands. 
One potential way to develop such skills is by designing activities in AI and robotics that are appropriately introduced in development stages \cite{bers2008, bers-horn2010, kazakoff-bers2012} as well as the development of grasping and understanding mathematical concepts (e.g. numbers, size, and shapes) \cite{bers2012, resnick1998}.
Similarly, Elkin et al. (2014) \cite{elkin2014}, for instance, explained how Robotics can provide a way to engage children in problem-solving activities based on Montessori education as well as design activities that allow children to participate in creative explorations, develop fine motor skills, hand-eye coordination, engage in collaborative and teamwork activities.

That said, figure \ref{fig:tm}(a) illustrate the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}.

%Finding solutions together translate to social situations as well as it provides children with the foundations for decision making, logical reasoning, categorizing, analytical thinking, negotiation, and creativity. 
%In that way, AIR4Children's workshop integrates various hands-on activities where the children will develop different intellectual and social skills to incorporate into other areas of their lives.
%More specifically, such workshops are based on several Montessori principles such as: moving from the simple to the complex, the concrete to the abstract, the familiar to the unfamiliar and the general to the specific, as well as a mixed age group, where children can learn from each other.
\begin{figure}[h]
  \centering
  \includegraphics[width=\linewidth]{../figures/teaching-materials/versions/drawing-v00.png}
  \caption{(a) Spiral learning divided into lecture, virtual and physical laboratory and connected via project to next session \cite{tarik2017} (b) robot assembly and (c) block-like programming style.}
  %\Description{.}
  \label{fig:tm}
\end{figure}

@@

\section{Conclusions and future work}
We introduced the term air4project as a project with the aim to tackle aspects for inclusion, accessibility, transparency, equity, fairness and participation of children in the fields of AI and Robotics as well as to create a more child-centre approach for AI and Robotics.
In this work, we also touched on the open source projects in AI and Robotics as a corner stone for AIR4Children with the aim of minimise cost of the materials and made customised educational material.  
Similarly, it has been presented the three phases for AIR4Children for piloting, implementing and refining workshops for children in the age range between 6 to 14. 
We also touched on the creation of curriculums with Montessori education, a non-traditional educational approach to help young audiences to develop skills such as think creatively with curiosity and open-minded as well as develop a have a sense of wonder and joy in learning.
